LV2

### 2018-05-09 paper.tex
Topics

>>>>

\section{Topics}
\label{sec:topics}

To investigate the collection further nine topics of interests were defined. The collection was manually searched using keywords to get relevant tweets. The topics are
\begin{itemize}
\item \texttt{LV001: Winter} Everything about winter. The relevant tweets are mostly about the weather, the pictures of snow and driving conditions.
\item \texttt{LV002: Mel\=anijas hronika} Mel\=anijas hronika is a Latvian movie that was selected for Foreign-Language Category for Oscars.
\item \texttt{LV003: Refugees} A broad topic about refugee crisis in Europe, attitude to immigration and immigrants.
\item \texttt{LV004: Dv\=eese\c{l}u putenis} A Latvian movie that is currently in production.
\item \texttt{LV005: Hockey} Ice hockey related tweets.
\item \texttt{LV006: Christmas} Christmas.
\item \texttt{LV007: New Year} New Year.
\item \texttt{LV008: Olympics} Tweets about the Olympic games and the Latvian team.
\item \texttt{LV009: Brexit} Brexit.
\end{itemize}
